---
title: "Documentation for famove package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Documentation for famove package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# General informations

This package is buld as part of final assignment in [Coursera](https://www.coursera.org/) course [Building R Packages](https://www.coursera.org/learn/r-packages) by Johns Hopkins University. The functions were provided in the course.

The goal of this document is introduce the famove package. The main purpose of famove is to summarize and map fatal motor vehicle accidents in the US by year.

## Summary

Summary of the number of people killed in motor vehicle accidents in the US by given year per month can be performed with the `fars_summarize_years` function.

Map the location of fatal motor vehicle accidents in selected state in the US by given year can be produced with the `fars_map_state` function.

```{r eval=FALSE}
fars_summarize_years(2014)
fars_map_state(5,2014)
```

